### 2020-01-27 docs/ANE2020/contents.tex
ANE2020 tex file update

Fig.~\ref{fig:slab-fluxes} shows the fast and thermal fluxes calculated by diffusion, CMFD, pCMFD and S$_16$ of the left half slab. The abscissa shows values of the group-dependent neutron mean free path (mfp) $\tau$.

@@

One or two mpf's from the boundary towards the center of the slab are enough for diffusion, to match well the reference S$_16$ results. On the other hand, closer to the boundary, the Ronen method shows better results. The flux deviations of the left half slab, are shown in Fig.~\ref{fig:flx_err_homg}, calculated by $\Delta\keff = \left(\keff^{-1}-k_{\text{ref}}^{-1}\right)\times 10^5$ pcm.

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_rho_I400_RMitr250.pdf}	
	\caption{Convergence of the reactivity along 250 Ronen iterations, with respect to S$_N$.}
	\label{fig:rho_homg}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_LB_I400_RMitr250.pdf}
	\caption{Deviation of the fluxes at the left-most cell, calculated by RM-CMFD and RM-pCMFD codes, with respect to the reference solution after 250 Ronen iterations.}
	\label{fig:slab-fluxes-dev}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_dD_I400_RMitr250.pdf}
	\caption{The Ronen method correction factors ($\delta D$), calculated by CMFD code, and ($\delta D^+, \delta D^-$), calculated by pCMFD code. Results shown here after 250 Ronen iterations.}
	\label{fig:slab-RM-corr-factor}
\end{figure}

>>>>

Fig.~\ref{fig:slab-fluxes} shows the fast and thermal fluxes calculated by diffusion, CMFD, pCMFD and S$_{16}$ of the left half slab. The abscissa's values are the group-dependent neutron mean free path (mfp) $\tau$. One or two mpf's from the boundary towards the center of the slab are enough for diffusion, to match well the reference S$_16$ results. On the other hand, closer to the boundary, the Ronen method shows better results.

@@

In Fig~\ref{fig:flx_err_homg}, the flux deviation (calculated by $\Delta \phi = \left[\left(\phirm-\phiref\right)/\phiref\right]\times 100$) at the first 40 cells of the left slab has approximately $\sim 20\%$ difference between diffusion and RM calculations. The difference observed closer to the boundary, due to the fact that the major transport effect occur near the boundary of the homogeneous slab.

@@

A comparison of the flux deviation, calculated by the two implementations of the RM, within the left-most (I=0) cell is shown in Fig.~\ref{fig:slab-fluxes-dev-LB}. The deviation of CMFD and pCMFD has very close trend along the 250 iterations, reaching approximately $\sim 2\%$ compared to the reference solution.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_LB_I400_RMitr250.pdf}
	\caption{Deviation of the fluxes at the left-most cell, calculated by RM-CMFD and RM-pCMFD codes, with respect to the reference solution after 250 Ronen iterations.}
	\label{fig:slab-fluxes-dev-LB}
\end{figure}

In Fig~\ref{fig:rho_homg}, the behavior of the eigenvalue difference $\Delta\keff$ in pcm, along RM iterations are represented, and calculated by $\Delta\keff = \left(\keff^{-1}-\kref^{-1}\right)\times 10^5$ pcm. The value of the eigenvalues reported by the reference S$_{16}$ solution is  $\kref = 0.74441$,  and by diffusion calculation $\keff = 0.74133$, which gives the value $\Delta\keff \approx 558$ pcm. One RM iteration resulting in tens of pcm, but CMFD perform well than pCMFD at the very first few iterations. After a steep decline of $\Delta\keff$, achieving by 10 iterations, both numerical implementations converging at the same rate, with a typical linear equation, approximated by $\Delta\keff \approx 4.545\cdot 10^-7 \times (\#\text{it}) + 0.744363$, it stands for iteration.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_dk_I400_RMitr250.pdf}	
	\caption{Convergence of the reactivity along 250 Ronen iterations, with respect to S$_N$.}
	\label{fig:rho_homg}
\end{figure}

The correction factors of CMFD and pCMFD (denoted by $\dd$, $dD^{+\setminus -}$, respectively) are shown in Fig~\ref{fig:slab-RM-dD}.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_dD_I400_RMitr250.pdf}
	\caption{The Ronen method correction factors ($\delta D$), calculated by CMFD code, and ($dD^{+\setminus -}$), calculated by pCMFD code. Results shown here after 250 Ronen iterations.}
	\label{fig:slab-RM-dD}
\end{figure}
